---
title: "gtsummary in quarto"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
#| echo: true             
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

```{r}
#| label: tbl-sex
#| tbl-cap: "Descriptive statistics by sex"
tbl_summary(
 nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

The descriptive statistics are shown stratified by sex @tbl-sex

```{r}
mean_sleep_weekend <- mean(nlsy$sleep_wknd, na.rm = TRUE)
mean_sleep_weekend
```

people slept an average of `r mean_sleep_weekend` hours

```{r}
#| label: tbl-one
#| tbl-cap: "This is a great table"
knitr::kable(mtcars)
```

```{r}
#| label: fig-hist
#| fig-cap: "This is a histogram"
hist(rnorm(100))
```

Cross-referencing

@tbl-one contains table ans @fig-hist contains histogram

InlineR

`r 10+5` things to do

`r nrow(nlsy)` participants

```{r}
total_sample <- nrow(nlsy)
```

there were `r total_sample` participants

```{r}
stats <- list(n = nrow(nlsy),
              mean_age = mean(nlsy$age_bir, na.rm = TRUE))
stats 
```

There were `` `r stats$n` `` participants with a mean age of `` `r stats$mean_age` ``.

`r mean(nlsy$age_bir, na.rm = TRUE)` is the mean

`r median(nlsy$age_bir, na.rm = TRUE)` is the median

```{r}
library(gtsummary)
```
